---
title: "Milestone 3"
author: "Molly Chiang"
date: "10/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(readr)
library(knitr)
library(janitor)
library(tidyverse)

```

## Milestone 3

The data I have loaded in this document is data from airbnb in New York City and London. The data consists of names of the listings, neighborhoods, lengths of stay, prices, number of reviews, host names and more. 

I got the data on New York data from a csv that I downloaded from the site Kaggle. I got the London data directly from the airbnb data repository on their website. 

So far, I have just loaded the data and explored the datasets a bit in my console (view, sample, glimpse, etc). However, I plan to integrate the two sets of London data (and maybe also integrate with the New York data?) and do some sort of analysis of different neighborhoods in the cities and the prices of airbnbs in those areas,and maybe the lengths of stay in those areas. I may also download more data from airbnb about different cities to compare with as well. I could also potentially compare the airbnb prices with real estate prices in the area (to see how they compare), but that would of course require finding real estate prices (maybe from NYC data base or zillow?). 


Here are the neighborhoods and prices of the most expensive NY Airbnbs:
```{r data_load}

ny_data <- read_csv("AB_NYC_2019.csv")
london_listings <- read_csv("listings.csv")
london_reviews <- read_csv("reviews.csv")

ny_data %>%
  select(neighbourhood_group, neighbourhood, price) %>%
  arrange(desc(price)) %>%
  head(10) %>%
  kable()
  
```


